---
title: "Lab 00 - Hello IDS!"
author: "Alexander"
date: "`r Sys.Date()`"
output: html_document
---

### Load packages and data

```{r load-packages, message=FALSE}
library(tidyverse) 
```

### Exercises 16-17

We set up the data frame. Edit the data below to include information about your team members.

```{r setup-tibble}
team_data <- tibble(
  name = c("Alexander", "Adam", "Jessica", 
           "Amy", "Harry"),
  github_username = c("AlexanderDug", "Adam-Smit05", "jessicapart", 
                      "amyha11", "harryj0603"), 
  colour = c("chartreuse", "green4", "green", 
             "blue", "orange"),
  hobby = c("Hockey", "Playing Guitar", "Rowing", 
            "Rock Climbing", "Chess"),
  favourite_number = c(3, 7, 8, 7, 7)
  )

team_data

 
```

### Exercise 18

We now work on visualising our data. 

```{r bar-plot}
p1 <- ggplot(data = team_data, 
             mapping = aes(x = github_username, 
                           y = favourite_number,
                           fill = colour), 
             ) +
   geom_col() +
   scale_fill_identity()
p1
```


3 of the 5 peoples favourite colour and number is green and 7 respectively

### Exercises 19

Change the text of the plot title and axis labels.

```{r labelled-bar-plot}
p1 + labs(x = "Names", 
          y = "Favourite Number",
          title = "Favourite Number of Different People")
```

Labs is used to rename axis and give other such titles

### Exercise 20

```{r new-bar-plot}
p2 <- ggplot(team_data, aes(x = hobby)) +
  geom_bar()
p2
```

Seen as everyone is spread across different hobbies, it is difficult to show the spread of hobbies with a bar chart because it will likely be very flat with a couple spikes. Bar charts would also end up being really long with all the different inputted values. I believe a pie chart would be a better choice as it is a more compact way of displaying the data and can easily show if any hobbies are more popular. 
